---
title: "About"
output:
  html_document:
    code_folding: hide
---

Greetings everyone and welcome to my about page.  For starters, i'm a newly graduated data scientist who's actively seeking employment. Feel free to reach out with any opportunities. 


To start us off, I've included a quick ggplot2 chart (my favorite graphing library) of places I've lived in my life. 


```{r PlacesLived}
shhhh <- suppressPackageStartupMessages

shhhh(library(tidyverse))
shhhh(library(ggplot2))
shhhh(library(dplyr))
shhhh(library(mapproj))
df <- read.csv('https://raw.githubusercontent.com/Landcruiser87/Andy_Heroy_Data_Science/gh-pages/data/Livingspaces.csv')

colnames(df) <- c("Place","City","State","Lat","Long","Year","cnt")

US <- map_data("world") %>% filter(region=="USA")

ggplot() + 
 geom_polygon(data = US, aes(x=long, y = lat, group = group), fill="grey", alpha=0.3) +
 geom_point(data=df, aes(x=Long, y=Lat, size=cnt, color=cnt)) +
 geom_text(aes(x=df$Long, y=df$Lat,label=df$City), size=3, nudge_x=0, nudge_y=1.3, check_overlap = T) +
 coord_map() +
 ylim(20,50) +
 xlim(-130,-60) +
 labs(title="Where I've called home",color="years") +
 scale_size_continuous(guide = FALSE) +
 theme(legend.position = c(0.9,0.4))


```

```{r}


```
## Things that peak my interest/take up my time.

  - Python
  - R
  - Machine Learning 
  - Deep Learning
  - Visualizations
  - Database Administration
  - Dashboards are awesome
  - Golf
  - Travel
  - Home Exercise
  - Rhodesian Ridgebacks
  - Fighting covid through Data Science

## Brief Timeline

  - 2004 - Graduate from Kenyon College 
  - 2004 - Work for a Toyota Atlantic Race Team in San Francisco
  - 2007 - New job at Cleveland Golf in Huntington Beach, CA
  - 2011 - New job at Titleist and move to Carlsbad, CA
  - 2015 - New job at Cobra-Puma Golf in Carlsbad, CA
  - 2018 - Move to Nebraska and start graduate school at SMU in Data Science
  - 2020 - Graduate and move too.......?
