---
title: "About"
---

Greetings everyone and welcome to my about page.  For starters, i'm a newly graduated data scientist who's actively seeking employment. Feel free to reach out with any opportunities. 


## Where I've lived. 

```{r PlacesLived}

library(plotly)
library(ggplot2)
library(dplyr)
df <- read.csv('https://raw.githubusercontent.com/Landcruiser87/Andy_Heroy_Data_Science/gh-pages/data/Livingspaces.csv')

colnames(df) <- c("Place","City","State","Lat","Long","Year","cnt")

library(maptools)
library(mapproj)
library(rgeos)
library(rgdal)
library(ggplot2)

# for theme_map
devtools::source_gist("33baa3a79c5cfef0f6df")

# nice US map GeoJSON
us <- readOGR(dsn="http://eric.clst.org/wupl/Stuff/gz_2010_us_040_00_500k.json", layer="OGRGeoJSON")

# even smaller polygons
us <- SpatialPolygonsDataFrame(gSimplify(us, tol=0.1, topologyPreserve=TRUE), 
                               data=us@data)

# don't need these for the continental base map
us <- us[!us$NAME %in% c("Alaska", "Hawaii", "Puerto Rico", "District of Columbia"),]

# for ggplot
map <- fortify(us, region="NAME")

# your data
myData <- data.frame(name=c("Florida", "Colorado", "California", "Harvard", "Yellowstone"),
                     lat=c(28.1, 39, 37, 42, 44.6), 
                     long=c(-81.6, -105.5, -120, -71,-110),
                     pop=c(280, 156, 128, 118, 202))

# the map

gg <- ggplot()
# the base map
gg <- gg + geom_map(data=map, map=map,
                    aes(x=long, y=lat, map_id=id, group=group),
                    fill="#ffffff", color="#0e0e0e", size=0.15)
# your bubbles
gg <- gg + geom_point(data=myData, 
                      aes(x=long, y=lat, size=pop), color="#AD655F") 
gg <- gg + labs(title="Bubbles")
# much better projection for US maps
gg <- gg + coord_map(projection="albers", lat=39, lat1=45)
gg <- gg + theme_map()
gg <- gg + theme(legend.position="bottom")
gg <- gg + theme(plot.title=element_text(size=16))
gg


```

```{r}
library(plotly)
library(ggplot2)
library(dplyr)
df <- read.csv('https://raw.githubusercontent.com/plotly/datasets/master/2011_february_us_airport_traffic.csv')

# geo styling
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showland = TRUE,
  landcolor = toRGB("gray95"),
  subunitcolor = toRGB("gray85"),
  countrycolor = toRGB("gray85"),
  countrywidth = 0.5,
  subunitwidth = 0.5
)

fig <- plot_geo(df, lat = ~lat, lon = ~long)
fig <- fig %>% add_markers(
    text = ~paste(airport, city, state, paste("Arrivals:", cnt), sep = "<br />"),
    color = ~cnt, symbol = I("square"), size = I(8), hoverinfo = "text"
  )
fig <- fig %>% colorbar(title = "Incoming flights<br />February 2011")
fig <- fig %>% layout(
    title = 'Most trafficked US airports<br />(Hover for airport)', geo = g
  )

fig
```




## Things that peak my interest/take up my time.

  - Python
  - R
  - Machine Learning 
  - Deep Learning
  - Visualizations
  - Database Administration
  - Dashboards are awesome
  - Golf
  - Travel
  - Home Exercise
  - Rhodesian Ridgebacks
  - Fighting covid through Data Science

## Brief Timeline

  - 2004 - Graduate from Kenyon College 
  - 2004 - Work for a Toyota Atlantic Race Team in San Francisco
  - 2007 - New job at Cleveland Golf in Huntington Beach, CA
  - 2011 - New job at Titleist and move to Carlsbad, CA
  - 2015 - New job at Cobra-Puma Golf in Carlsbad, CA
  - 2018 - Move to Nebraska and start graduate school at SMU in Data Science
  - 2020 - Graduate and move too.......?
